\RequirePackage{pdfmanagement}
\documentclass[a4paper,extrafontsizes,oneside]{memoir}

\usepackage{amsmath}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    citecolor=ForestGreen,
    linkcolor=NavyBlue,
    filecolor=magenta,
    urlcolor=BrickRed
}
\usepackage{microtype}
\usepackage{pdfpages}
\usepackage{newpax}

\setlrmarginsandblock{1in}{1in}{*}
\setulmarginsandblock{0.8in}{*}{1}
\checkandfixthelayout

\makeindex

\title{Preproceedings of the XXnd International Conference on Types for Proofs and Programs (TYPES 20XX)}

\author{XX and XX}

\pagestyle{empty}

\begin{document}

\hypersetup{pageanchor=false}
\pagenumbering{gobble}

{
\calccentering{\unitlength}
\begin{adjustwidth*}{\unitlength}{-\unitlength}

  \phantom{m}

  \vspace{1cm}

  \begin{center}
    {\LARGE XX$^{\text{st}}$ International Conference on \\ Types for Proofs and Programs \par}
  \end{center}

  \vspace{0.8cm}

  \begin{center}
    {\HUGE TYPES 20XX}
  \end{center}

  \vspace{0.8cm}

  \begin{center}
    {\LARGE An XX}
  \end{center}

  \vspace{1.2cm}

  \begin{center}
    {\Huge \noindent Abstracts}
  \end{center}

  \vspace{2cm}

  \begin{center}
    Some picture
  \end{center}

  \vspace{1.8cm}

  \begin{center}
    {\LARGE Z University, Earth, 4--8 May 20XX \par}
  \end{center}

  \vspace{2.5cm}

  Space for sponsor images

\end{adjustwidth*}
}

\clearpage

%% copyrightpage
\begingroup
\footnotesize
\parindent 0pt
\parskip \baselineskip

32$^{\text{st}}$ International Conference on Types for Proofs and Programs \\
TYPES 20XX \\
An XX \\
Z University, Earth, Sweden, 4--8 May 20XX \\
Abstracts \\
\url{https://example.com}

\vspace{2\baselineskip}

Edited by XX and XX.

\vspace{2\baselineskip}

Department of XX \\
Z University \\
Earth \\

\vspace{4\baselineskip}

\textcopyright{} 20XX the authors and the editors.

\vspace{1\baselineskip}

Title photo by XX

\endgroup

\clearpage

\addtocounter{page}{-2}
\hypersetup{pageanchor=true}

\frontmatter

\chapter{Preface}

The TYPES meetings are a forum to present new and ongoing work in all aspects of type theory and its applications, especially in formalized and computer-assisted reasoning and computer programming.
In the spirit of workshops, talks may be based on newly published papers, work submitted for publication, but also work in progress.

This year, 69 abstracts were submitted, and each submission was reviewed by at least three program committee members.
62 abstract were accepted for short presentations (20 minute slots), of which 2 were withdrawn before the conference.
The programme was complemented by five long invited presentations (60 minute slots): XX

The conference received financial support from XX.
We gratefully acknowledge all support.

Similarly to previous years, a formal post-proceedings volume in Dagstuhl’s \emph{Leibniz International Proceedings in Informatics (LIPIcs)} series is planned for after the conference; papers submitted to that volume need not have been selected for presentation at the conference, but must represent unpublished work, and are subjected to (another) full peer-review process.

\vspace{1em}

\noindent May 20XX, Gothenburg\hfill XX and XX

\openany

\chapter{Organisation}

\input{committees}

\section*{Sponsors}

\begin{tabular}{@{}l@{\qquad}l}
  \emph{Main sponsor} &
  XX \\[1ex]
  \emph{Gold} &
  XX \\[1ex]
  \emph{Silver} &
  XX \\
  &
  XX \\[1ex]
  \emph{Bronze} &
  XX \\
  &
  XX  \\
\end{tabular}

% \begin{tabular}{@{}ll}
%   XX & (\emph{Gold sponsor}) \\
%   XX & (\emph{Silver sponsor})\\
%   XX & (\emph{Silver sponsor})\\
%   XX  & (\emph{Bronze sponsor})\\
%   XX{Bronze sponsor})\\
% \end{tabular}

\clearpage

\setcounter{tocdepth}{2}
{
  \renewcommand{\aftertoctitle}{\par\nobreak \mbox{}{\normalfont \normalsize An alphabetical index of all authors can be found on page~\pageref{indexpage}.}\par\nobreak}
  \small
  \tableofcontents
}

\clearpage

\mainmatter

\input{core}

\renewcommand{\indexname}{Author index}
\phantomsection\label{indexpage}
\printindex
\end{document}
